About

### 2024-09-18 about.qmd
Fix heading level
The title is already level 1, hence
all headings need to start with level 2.
Remove email address by Josephine
As it is outdated

---
title: "About"
author:
  - name: "Florian Kohrt"
    orcid: "0000-0003-0374-5625"
  - name: "Josephine Zerna"
    email: "josephine.zerna@tu-dresden.de"
    orcid: "0000-0003-2892-884X"
  - name: "Christoph Scheffel"
    email: "christoph_scheffel@tu-dresden.de"
    orcid: "0000-0001-5963-9229"
bibliography: grateful-refs.bib
---

# Utilized Software

@@

# License and Disclaimer

@@

# Funding

>>>>

---
title: "About"
author:
  - name: "Florian Kohrt"
    orcid: "0000-0003-0374-5625"
  - name: "Josephine Zerna"
    orcid: "0000-0003-2892-884X"
  - name: "Christoph Scheffel"
    email: "christoph_scheffel@tu-dresden.de"
    orcid: "0000-0001-5963-9229"
bibliography: grateful-refs.bib
---

## Utilized Software

@@

## License and Disclaimer

@@

## Funding
